fdcoexist

### 2018-09-04 paper_simulations.Rmd
Equations typo fixed.
:memo: added titles to Rmd
Updated variance graph

# Generate traits --------------------------------------------------------------
# Make traits with different correlations
set.seed(1)
uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                   cor_coef = 0)
set.seed(1)
low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                     cor_coef = 0.3)

set.seed(1)
high_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                      cor_coef = 0.7)

@@

The equation above only considers inter-specific competition when $j \neq i$ in the sum. We can however add intra-specific competition when $j = i$. Each site has a species-specific carrying capacity $K$ as the number of individuals approaches this carrying capacity the intra-specific competition increases:
\begin{equation}
\alpha_{ii} = B \times \N_{t,i,x}
\end{equation}

@@

\begin{equation}
N_{t+1, i, x} = \frac{
k \times \exp\left(- \displaystyle\frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right) \times N_{t, i, x}}{
1 + A \times \displaystyle\sum_{j = 1,~j \neq i}^{S} N_{t, j, x}  (1 - \delta_{ij}) +
B \times \N_{t,i,x}
}
\end{equation}

@@

@@

@@

@@

# CWV against environment

>>>>

# Generate traits --------------------------------------------------------------
trait_seed = 5
# Make traits with different correlations
set.seed(trait_seed)
uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                   cor_coef = 0)
set.seed(trait_seed)
low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                     cor_coef = 0.3)

set.seed(trait_seed)
high_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                      cor_coef = 0.7)

@@

The equation above only considers inter-specific competition when $j \neq i$ in the sum. We can however add intra-specific competition when $j = i$. Each site has a species-specific carrying capacity $K$ as the number of individuals approaches this carrying capacity the intra-specific competition increases:
\begin{equation}
\alpha_{ii} = B \times N_{t,i,x}
\end{equation}

@@

\begin{equation}
N_{t+1, i, x} = \frac{
k \times \exp\left(- \displaystyle\frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right) \times N_{t, i, x}}{
1 + A \times \displaystyle\sum_{j = 1,~j \neq i}^{S} N_{t, j, x}  (1 - \delta_{ij}) +
B \times N_{t,i,x}
}
\end{equation}

@@

## R² CWM against environment

@@

## Trait variance against environment

@@

ggplot(all_trait_var, aes(scenario, trait_value, fill = fct_rev(cor_level))) +
    geom_boxplot() +
    facet_grid(rows = vars(env_width, compet_status),
               cols = vars(trait_name),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength")),
               scales = "free_y") +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(y = "Variance of trait across all patches")

@@

## CWV against environment
